Deciding to Disclose

### 2015-06-04 Background.tex
Clarify GT -> BGT -> SG in bg

The majority of classical game theory focuses on strategic decision making, in scenarios where all players have complete information about all aspects of the game. An alternative, perhaps more common situation, is that players have incomplete information, i.e. their knowledge of the state of the world is in some way deficient. \citet{Harsanyi1967} introduced the concept of a Bayesian game, resolving the problems introduced by the incomplete information scenario by allowing the possible variations on the rules to be treated as subgames. This adds an additional player - nature, to the game, where nature takes the first move thereby deciding which subgame is played. Nature is assumed to make their move by lottery, and where the probability distribution governing the lottery is known to all players this permits the game to be formulated as one of complete information.

Here, we are specifically interested in signalling games \citep{Spence1973,Kreps1987}, where one player holds some private information which may be communicated (or not) by means of a signal.
This basic form has been widely applied, with substantial interest in what conditions permit honest signalling as Nash equilibria or \acp{ESS}. \citet{Grafen1990}, following from a suggestion by \citet{Zahavi1975}, proposed that if signals intended to indicate mate quality exacted a cost on the signaller (e.g. peacock tail feathers), then honest signalling would constitute an \ac{ESS}. Similar results have also been demonstrated in a game of job market signalling, where signal cost was differentiated by type \citep{Spence1973}. 
Costly signalling has also been suggested as an explanation of behaviour that at first glance appears counter intuitive, for example \citet{Godfray1991} applied the idea to the food solicitation behaviour of chicks, where a stronger signal (i.e. more, or louder chirping) carries a risk of being eaten by predators. Moving beyond animal behaviour, \citet{Sosis2003} considered the implications of ritual behaviour, in the context of religion, representing a costly signal, an idea subsequently extended by \citet{Henrich2009} to include cultural transmission, and \citet{Wildman2011} to introduce group differentiation.

>>>>

The majority of classical game theory focuses on strategic decision making, in scenarios where all players have complete information about all aspects of the game and their opponents. Moves by players are assumed to be perfectly rational, and account for the equally rational moves of their opponents.
An alternative, perhaps more common situation, is that players have incomplete information, whether about the actions available to their opponents or themselves, or concerning the possible payoffs for the players.   
This second case was essentially unexplored, until \citet{Harsanyi1967} introduced the concept of a Bayesian game, which treats incomplete information scenarios by allowing the possible variations on the rules to be treated as subgames. This adds an additional player - nature, to the game, where nature takes the first move thereby deciding which subgame is played. Nature is assumed to make their move by lottery, and where the probability distribution governing the lottery is known to all players this permits the game to be formulated as one of complete information.

Here, we are specifically interested in signalling games \citep{Spence1973,Kreps1987}, a type of Bayesian game where one player holds some private information which may be communicated (or not) by means of a signal.
This basic form has been widely applied, with substantial interest in what conditions permit honest signalling as Nash equilibria or \acp{ESS}. \citet{Grafen1990}, following from a suggestion by \citet{Zahavi1975}, proposed that if signals intended to indicate mate quality exacted a cost on the signaller (e.g. peacock tail feathers), then honest signalling would constitute an \ac{ESS}. Similar results have also been demonstrated in a game of job market signalling, where signal cost was differentiated by type \citep{Spence1973}. 
Costly signalling has also been suggested as an explanation of behaviour that at first glance appears counter intuitive, for example \citet{Godfray1991} applied the idea to the food solicitation behaviour of chicks, where a stronger signal (i.e. more, or louder chirping) carries a risk of being eaten by predators. Moving beyond animal behaviour, \citet{Sosis2003} considered the implications of ritual behaviour, in the context of religion, representing a costly signal, an idea subsequently extended by \citet{Henrich2009} to include cultural transmission, and \citet{Wildman2011} to introduce group differentiation.
